---
title: "Portfolio 10"
author: "Conor Lacey"
date: "2023-04-26"
output: html_document
runtime: shiny
---

```{r libraries}
suppressWarnings(
  suppressMessages(
    c(
    library(shiny),
    library(tidyverse),
    library(rsconnect)
    )
  )
)
```

### Introduction

Alright for a my last portfolio I am going to be making a shiny app for Eric. Specifically I am going to make a z-distribution that will be able to shade in the p-values and display the alpha cut-off rejection regions.

Now shiny is a whole different ball game for r, so I'm going to start off very simple and work our way up to more difficult tasks for this project.

### Normal Distribution

Let's begin by making sure we can create a normal distribution in the app.

```{r Normal Distribution}
ui <- fluidPage(
    titlePanel("Z-Distribution"),
    mainPanel(plotOutput("distPlot"))
)

server <- function(input,output){
  x <- seq(-4,4, length.out = 1e4)
  y <- dnorm(x)
  
  dat <- data.frame( x = x, y = y) #Normal Dist. Data
  
    graph <- dat %>% ggplot(aes(x = x, y = y)) +
    geom_line(color = "blue", linewidth = 1) +
    ylab("Density") +
    xlab("Z") + 
    theme_classic() +
    theme(axis.title = element_text(size = 20),
          axis.text = element_text(size = 15))
    
    output$distPlot <- renderPlot({graph})
}

# Run the application 
shinyApp(ui = ui, server = server)
```

### Slider Input

Perfect now let's add a slide input for the z-value as well as textoutput for the z-value. We will also shade in the p-value region and display the p-value.

```{r slider Input}
ui <- fluidPage(
  
  # Application title
  titlePanel("Z-Distribution"),
  
  sidebarLayout(
    sidebarPanel(
      
      sliderInput(inputId = "z",   #Sliding Bar
                  label = "Z Value",
                  min = -4,
                  max = 4,
                  value = 0,
                  step = 0.01)
    ),
    
    # Sidebar with a slider input for number of bins 
    # Show a plot of the generated distribution
    mainPanel(
      plotOutput("distPlot"),
      h4(textOutput("text1")),
    )
  )
)

server <- function(input, output) {
  
  x <- seq(-4,4, length.out = 1e4)
  y <- dnorm(x)
  
  dat <- data.frame( x = x, y = y) #Normal Dist. Data
  
  graph<- dat %>% ggplot(aes(x = x, y = y)) +
    geom_line(color = "blue", linewidth = 1) +
    ylab("Density") +
    xlab("Z") + 
    theme_classic() +
    theme(axis.title = element_text(size = 20),
          axis.text = element_text(size = 15))
  
  shade = 0.5
  
  dottedlinesize = 1
  

  observe({
    
      x <- seq(input$z,4, length.out = 1e4)
      y <- dnorm(x)
      x <- c(x,rev(x))
      y <- c(y,rep(0, 1e4))
      
      tail <- data.frame(x = x, y = y)
      
      graph <- graph + geom_polygon(data = tail,
                                    fill = "#36b8f5", alpha = shade) 
      
      output$text2 <- renderText(
        paste("P-value = ",
              integrate(dnorm, input$z, Inf)$value %>% round(digits = 3) %>% as.character())
      )

      output$distPlot <- renderPlot({graph})
      
    })
  
  output$text1 <- renderText(
            paste("-value = ",
              input$z %>% round(digits = 3) %>% as.character())
            
  )

}

# Run the application 
shinyApp(ui = ui, server = server)
```

### Select Direction

Alright now how about we specify the direction of our p-value.

```{r select direction}
ui <- fluidPage(
  
  # Application title
  titlePanel("Z-Distribution"),
  
  sidebarLayout(
    sidebarPanel(
      
      selectInput(inputId = "direction", 
                  label = "Direction:",
                  choices = list("Right Tail", "Left Tail", "Two-Tailed")),
      
      
      sliderInput(inputId = "z",   #Sliding Bar
                  label = "Z Value",
                  min = -4,
                  max = 4,
                  value = 0,
                  step = 0.01),
    ),
    
    # Sidebar with a slider input for number of bins 
    # Show a plot of the generated distribution
    mainPanel(
      plotOutput("distPlot"),
      h4(textOutput("text1")),
      h4(textOutput("text2"))
    )
  )
)

server <- function(input, output) {
  
  x <- seq(-4,4, length.out = 1e4)
  y <- dnorm(x)
  
  dat <- data.frame( x = x, y = y) #Normal Dist. Data
  
  graph<- dat %>% ggplot(aes(x = x, y = y)) +
    geom_line(color = "blue", linewidth = 1) +
    ylab("Density") +
    xlab("Z") + 
    theme_classic() +
    theme(axis.title = element_text(size = 20),
          axis.text = element_text(size = 15))
  
  shade = 0.5
  
  dottedlinesize = 1
  

# Input Direction ---------------------------------------------------------

  observe({
    if(input$direction == "Right Tail"){
      
      x <- seq(input$z,4, length.out = 1e4)
      y <- dnorm(x)
      x <- c(x,rev(x))
      y <- c(y,rep(0, 1e4))
      
      tail <- data.frame(x = x, y = y)
      
      graph <- graph + geom_polygon(data = tail,
                                    fill = "#36b8f5", alpha = shade) 
      
      output$text2 <- renderText(
        paste("P-value = ",
              integrate(dnorm, input$z, Inf)$value %>% round(digits = 3) %>% as.character())
      )

      output$distPlot <- renderPlot({graph})
    }
    if(input$direction == "Left Tail"){
      
      x <- seq(input$z, -4, length.out = 1e4)
      y <- dnorm(x)
      x <- c(x,rev(x))
      y <- c(y,rep(0, 1e4))
      
      tail <- data.frame(x = x, y = y)
      
      graph <- graph + geom_polygon(data = tail,
                                    fill = "#36b8f5", alpha = shade)
    
      output$text2 <- renderText(
        paste("P-value = ",
              integrate(dnorm, -Inf, input$z)$value %>% round(digits = 3) %>% as.character())
      )
     
      output$distPlot <- renderPlot({graph})
    }

    if(input$direction == "Two-Tailed"){
      if (input$z >= 0){
        
        x <- seq(-input$z, -4, length.out = 1e4)
        y <- dnorm(x)
        x <- c(x,rev(x))
        y <- c(y,rep(0, 1e4))
        
        tailL <- data.frame(x = x, y = y)
        
        
        x <- seq(input$z, 4, length.out = 1e4)
        y <- dnorm(x)
        x <- c(x,rev(x))
        y <- c(y,rep(0, 1e4))
        
        tailR <- data.frame(x = x, y = y)
        
        graph <- graph + 
          geom_polygon(data = tailR,
                       fill = "#36b8f5", alpha = shade) + 
          geom_polygon(data = tailL,
                       fill = "#36b8f5", alpha = shade)
        
        output$text2 <- renderText(
          paste("P-value = ",
                (integrate(dnorm, input$z, Inf)$value*2) %>% round(digits = 3) %>% as.character())
        )
        

        output$distPlot <- renderPlot({graph})
      }
      
      if (input$z < 0 ){
        
        x <- seq(input$z, -4, length.out = 1e4)
        y <- dnorm(x)
        x <- c(x,rev(x))
        y <- c(y,rep(0, 1e4))
        
        tailL <- data.frame(x = x, y = y)
        
        
        x <- seq(-input$z, 4, length.out = 1e4)
        y <- dnorm(x)
        x <- c(x,rev(x))
        y <- c(y,rep(0, 1e4))
        
        tailR <- data.frame(x = x, y = y)
        
        graph <- graph + 
          geom_polygon(data = tailR,
                       fill = "#36b8f5", alpha = shade) + 
          geom_polygon(data = tailL,
                       fill = "#36b8f5", alpha = shade)
        
        output$text2 <- renderText(
          paste("P-value = ",
                (integrate(dnorm, -Inf, input$z)$value*2) %>% round(digits = 3) %>% as.character())
        )
        
        output$distPlot <- renderPlot({graph})
      }
    }
  })
  
  output$text1 <- renderText(
    paste("Z-value = ", {input$z}))
  
}

# Run the application 
shinyApp(ui = ui, server = server)
```

### Alpha Values

Alright and now the last thing I want to introduce are alpha values or the rejection thresholds that are typical in a statistical test. I will make another select input widget for this as well. 

```{r alpha values}
#
# This is a Shiny web application. You can run the application by clicking
# the 'Run App' button above.
#
# Find out more about building applications with Shiny here:
#
#    http://shiny.rstudio.com/
#

library(shiny)
library(tidyverse)
library(rsconnect)
library(ggpattern)

# Define UI for application that draws a histogram
ui <- fluidPage(
  
  # Application title
  titlePanel("Z-Distribution"),
  
  sidebarLayout(
    sidebarPanel(
      
      selectInput(inputId = "direction", 
                  label = "Direction:",
                  choices = list("Right Tail", "Left Tail", "Two-Tailed")),
      
      selectInput(inputId = "alpha",
                  label = "Alpha:",
                  choices = list("None", "0.05", "0.025")),
      
      sliderInput(inputId = "z",   #Sliding Bar
                  label = "Z Value",
                  min = -4,
                  max = 4,
                  value = 0,
                  step = 0.01),
    ),
    
    # Sidebar with a slider input for number of bins 
    # Show a plot of the generated distribution
    mainPanel(
      plotOutput("distPlot"),
      h4(textOutput("text1")),
      h4(textOutput("text2"))
    )
  )
)

server <- function(input, output) {
  
  x <- seq(-4,4, length.out = 1e4)
  y <- dnorm(x)
  
  dat <- data.frame( x = x, y = y) #Normal Dist. Data
  
  graph<- dat %>% ggplot(aes(x = x, y = y)) +
    geom_line(color = "blue", linewidth = 1) +
    ylab("Density") +
    xlab("Z") + 
    theme_classic() +
    theme(axis.title = element_text(size = 20),
          axis.text = element_text(size = 15))
  
  shade = 0.5
  
  dottedlinesize = 1
  

# Input Direction ---------------------------------------------------------

  observe({
    if(input$direction == "Right Tail"){
      
      x <- seq(input$z,4, length.out = 1e4)
      y <- dnorm(x)
      x <- c(x,rev(x))
      y <- c(y,rep(0, 1e4))
      
      tail <- data.frame(x = x, y = y)
      
      graph <- graph + geom_polygon(data = tail,
                                    fill = "#36b8f5", alpha = shade) 
      
      output$text2 <- renderText(
        paste("P-value = ",
              integrate(dnorm, input$z, Inf)$value %>% round(digits = 3) %>% as.character())
      )
      if(input$alpha == 0.05){
        al.L <- data.frame(x = c(1.645, 1.645), y = c(0, dnorm(1.645)))
        
        stripes <- data.frame(x = seq(1.645,))
        graph <- graph + 
          geom_line(data = al.L, aes(x = x, y = y), 
                                   color = "red", linetype = "dashed", 
                                   linewidth = dottedlinesize)
      }
      if(input$alpha == 0.025){
        al.L <- data.frame(x = c(1.96, 1.96), y = c(0, dnorm(1.96)))
        graph <- graph + geom_line(data = al.L, aes(x = x, y = y),
                                   color = "red", linetype = "dashed",
                                   linewidth = dottedlinesize)
      }

      output$distPlot <- renderPlot({graph})
    }
    if(input$direction == "Left Tail"){
      
      x <- seq(input$z, -4, length.out = 1e4)
      y <- dnorm(x)
      x <- c(x,rev(x))
      y <- c(y,rep(0, 1e4))
      
      tail <- data.frame(x = x, y = y)
      
      graph <- graph + geom_polygon(data = tail,
                                    fill = "#36b8f5", alpha = shade)
    
      output$text2 <- renderText(
        paste("P-value = ",
              integrate(dnorm, -Inf, input$z)$value %>% round(digits = 3) %>% as.character())
      )
      
      if(input$alpha == 0.05){
        al.L <- data.frame(x = c(-1.645, -1.645), y = c(0, dnorm(-1.645)))
        graph <- graph + geom_line(data = al.L, aes(x = x, y = y),
                                   color = "red", linetype = "dashed",
                                   linewidth = dottedlinesize)
      }
      if(input$alpha == 0.025){
        al.L <- data.frame(x = c(-1.96, -1.96), y = c(0, dnorm(-1.96)))
        graph <- graph + geom_line(data = al.L, aes(x = x, y = y),
                                   color = "red", linetype = "dashed",
                                   linewidth = dottedlinesize)
      }
     
      output$distPlot <- renderPlot({graph})
    }

    if(input$direction == "Two-Tailed"){
      if (input$z >= 0){
        
        x <- seq(-input$z, -4, length.out = 1e4)
        y <- dnorm(x)
        x <- c(x,rev(x))
        y <- c(y,rep(0, 1e4))
        
        tailL <- data.frame(x = x, y = y)
        
        
        x <- seq(input$z, 4, length.out = 1e4)
        y <- dnorm(x)
        x <- c(x,rev(x))
        y <- c(y,rep(0, 1e4))
        
        tailR <- data.frame(x = x, y = y)
        
        graph <- graph + 
          geom_polygon(data = tailR,
                       fill = "#36b8f5", alpha = shade) + 
          geom_polygon(data = tailL,
                       fill = "#36b8f5", alpha = shade)
        
        output$text2 <- renderText(
          paste("P-value = ",
                (integrate(dnorm, input$z, Inf)$value*2) %>% round(digits = 3) %>% as.character())
        )
        
        if(input$alpha == 0.05){
          al.L <- data.frame(x = c(-1.96, -1.96), y = c(0, dnorm(-1.96)))
          al.R <- data.frame(x = c(1.96, 1.96), y = c(0, dnorm(1.96)))
          graph <- graph + 
            geom_line(data = al.L, aes(x = x, y = y),
                      color = "red", linetype = "dashed",
                      linewidth = dottedlinesize) +
            geom_line(data = al.R, aes(x = x, y = y),
                      color = "red", linetype = "dashed",
                      linewidth = dottedlinesize) 
        }
        if(input$alpha == 0.025){
          al.L <- data.frame(x = c(-2.24, -2.24), y = c(0, dnorm(-2.24)))
          al.R <- data.frame(x = c(2.24, 2.24), y = c(0, dnorm(2.24)))
          graph <- graph + 
            geom_line(data = al.L, aes(x = x, y = y),
                      color = "red", linetype = "dashed",
                      linewidth = dottedlinesize) +
            geom_line(data = al.R, aes(x = x, y = y),
                      color = "red", linetype = "dashed",
                      linewidth = dottedlinesize)
        }

        output$distPlot <- renderPlot({graph})
      }
      
      if (input$z < 0 ){
        
        x <- seq(input$z, -4, length.out = 1e4)
        y <- dnorm(x)
        x <- c(x,rev(x))
        y <- c(y,rep(0, 1e4))
        
        tailL <- data.frame(x = x, y = y)
        
        
        x <- seq(-input$z, 4, length.out = 1e4)
        y <- dnorm(x)
        x <- c(x,rev(x))
        y <- c(y,rep(0, 1e4))
        
        tailR <- data.frame(x = x, y = y)
        
        graph <- graph + 
          geom_polygon(data = tailR,
                       fill = "#36b8f5", alpha = shade) + 
          geom_polygon(data = tailL,
                       fill = "#36b8f5", alpha = shade)
        
        output$text2 <- renderText(
          paste("P-value = ",
                (integrate(dnorm, -Inf, input$z)$value*2) %>% round(digits = 3) %>% as.character())
        )
        
        if(input$alpha == 0.05){
          al.L <- data.frame(x = c(-1.96, -1.96), y = c(0, dnorm(-1.96)))
          al.R <- data.frame(x = c(1.96, 1.96), y = c(0, dnorm(1.96)))
          
          graph <- graph + 
            geom_line(data = al.L, aes(x = x, y = y),
                      color = "red", linetype = "dashed",
                      linewidth = dottedlinesize) +
            geom_line(data = al.R, aes(x = x, y = y),
                      color = "red", linetype = "dashed",
                      linewidth = dottedlinesize) 
        }
        if(input$alpha == 0.025){
          al.L <- data.frame(x = c(-2.24, -2.24), y = c(0, dnorm(-2.24)))
          al.R <- data.frame(x = c(2.24, 2.24), y = c(0, dnorm(2.24)))
          graph <- graph + 
            geom_line(data = al.L, aes(x = x, y = y),
                      color = "red", linetype = "dashed",
                      linewidth = dottedlinesize) +
            geom_line(data = al.R, aes(x = x, y = y),
                      color = "red", linetype = "dashed",
                      linewidth = dottedlinesize)
        }
        
        output$distPlot <- renderPlot({graph})
      }
    }
  })
  
  output$text1 <- renderText(
    paste("Z-value = ", {input$z}))
  
}

# Run the application 
shinyApp(ui = ui, server = server)
```

Ta da! An easy to use z-distribution that Eric can use!
