---
title: "Portfolio 10"
author: "Conor Lacey"
date: "2023-04-26"
output: html_document
runtime: shiny
---

```{r libraries}
suppressWarnings(
  suppressMessages(
    c(
    library(shiny),
    library(tidyverse),
    library(rsconnect)
    )
  )
)
```

### Introduction

Alright for a my last portfolio I am going to be making a shiny app for Eric. Specifically I am going to make a z-distribution that will be able to shade in the p-values and display the alpha cut-off rejection regions.

Now shiny is a whole different ball game for r, so I'm going to start off very simple and work our way up to more difficult tasks for this project.

### Normal Distribution

Let's begin by making sure we can create a normal distribution in the app.

```{r Normal Distribution}
ui <- fluidPage(
    titlePanel("Z-Distribution"),
    mainPanel(plotOutput("distPlot"))
)

server <- function(input,output){
  x <- seq(-4,4, length.out = 1e4)
  y <- dnorm(x)
  
  dat <- data.frame( x = x, y = y) #Normal Dist. Data
  
    graph <- dat %>% ggplot(aes(x = x, y = y)) +
    geom_line(color = "blue", linewidth = 1) +
    ylab("Density") +
    xlab("Z") + 
    theme_classic() +
    theme(axis.title = element_text(size = 20),
          axis.text = element_text(size = 15))
    
    output$distPlot <- renderPlot({graph})
}

# Run the application 
shinyApp(ui = ui, server = server)
```


###
